---
title: "PS_1"
author: "Yonatan-Lourie"
date: "4/12/2021"
output:
  html_document:
    rmarkdown::html_document:
    theme: journal
---

```{r}
setwd("C:\\Users\\Admin\\Desktop\\Studies\\2nd, 2nd\\Applied econometrics\\PS1")
       
knitr::opts_chunk$set(warning=FALSE)
```

```{r, message=FALSE, results==hide, warning=FALSE}
library(magrittr)
library(haven)
library(Hmisc)
library(tidyverse)
library(ggplot2)
library(magrittr)
library(dplyr)
library(stargazer)
library(plyr)
library(ri)
library(scales)
```

## Part 1. Setup and Descriptive Statistics

### 1-2

```{r}
#1
df_ <- readRDS("earlytrainingproject_clean.rds") #Load the dataset.

#2
varsChild <- c("iq5", "iq6", "iq12", "retn12", "iep12")
varsTeen <- c("iq15", "hsgrad", "parent")
varsAdult <- c("college", "employed", "convicted", "felon", "jailed", "marijuana")

vars <- c(varsChild, varsTeen, varsAdult)

```

### 3-4

```{r}
#3
df_ <- df_[c("SUBJECT", "DC_TRT", "SEX", vars)]

#4
print(describe(df_))

```

### 5

```{r}
#5
#I've used sapply to sum how many nulls i have in each column (it feels like to messy eith the describe)
na_count <-sapply(df_, function(y) sum(length(which(is.na(y)))))
print(na_count)
df <- na.omit(df_)
na_count2 <-sapply(df, function(y) sum(length(which(is.na(y)))))
print(paste("Number of omitted observations: ", sum(na_count)-sum(na_count2)))

```

### 6

```{r}
describe(df$SEX)
```

### 7-8

```{r results='asis'}

#7
#create a new dummy variable that mapping treated and sex.
df$treat <- ifelse(df$DC_TRT=="Control", 0, 1)
df$fem <- ifelse(df$SEX=="F", 1, 0)

#8
stargazer(subset(df,treat==0)[vars],type="html",title="Descriptive Statistics, Control group", digits=2,covariate.labels=vars)

stargazer(subset(df,treat==1)[vars],type="html",title="Descriptive Statistics, Treated group", digits=2,covariate.labels=vars)
```

## Part 2. Estimates of Average Treatment Effects

#### Denote that the sign of the effect is changing between variables (we want less from jailed but more IQ)

### 1

```{r results='asis'}
#subsetting only the treated and not treated mean of vars
mean_treated = sapply(subset(df, df$treat==1)[c(vars)], mean)
mean_not_treated = sapply(subset(df, df$treat==0)[c(vars)], mean)

#making the dataframe
means_table = data.frame(mean_treated, mean_not_treated, effect=mean_treated-mean_not_treated)

stargazer(means_table, type="html",title="Estimated average treatment effects", digits=2,summary = FALSE, covariate.labels = c("Var","Mean treated", "Mean not treated", "Avrage treatment effect"))
```

### 2

```{r results='asis'}

#getting only treated and not treated boys mean of vars 
mean_treated_M = sapply(subset(df, df$treat==1 & df$fem==0)[c(vars)], mean)
mean_not_treated_M = sapply(subset(df, df$treat==0 & df$fem==0)[c(vars)], mean)

means_table_M = data.frame(mean_treated_M, mean_not_treated_M, effect=mean_treated_M-mean_not_treated_M)

stargzer_boys <-  stargazer(means_table_M, type="html",title="Estimated average treatment effects for boys", digits=2,summary = FALSE, covariate.labels = c("Var","Mean treated", "Mean not treated", "Avrage treatment effect"))

#getting only treated and not treated females mean of vars 
mean_treated_F = sapply(subset(df, df$treat==1 & df$fem==1)[c(vars)], mean)
mean_not_treated_F = sapply(subset(df, df$treat==0 & df$fem==1)[c(vars)], mean)

means_table_F = data.frame(mean_treated_F, mean_not_treated_F, effect=mean_treated_F-mean_not_treated_F)

stargazer_girls <- stargazer(means_table_F, type="html",title="Estimated average treatment effects for girls", digits=2,summary = FALSE, covariate.labels = c("Var","Mean treated", "Mean not treated", "Avrage treatment effect"))

```

## Part 3. Randomization Tests

### 1

```{r}
#the answer to everything
set.seed(42)

#making the permutations of the treat variable (should be 82choose41, but
# the genperms is making it smaller by approximation)
permutations <- genperms(df$treat, blockvar=NULL, clustvar=NULL)

#making the probabilty of treatment under randomization
probs <- genprobexact(df$treat, clustvar = df$SUBJECT)

unique(probs)
dim(permutations)
```

### 2

```{r}

EstFunc <- function(df, perms, prob, vars) {
  #first create Ates that will produce a function that take each column,
  #and making estimated average treatment effects (ATEs).
  Ates <- function(vec) {
    PotentialOutcome <- genouts(vec, df$treat)
    ATES <- gendist(PotentialOutcome, perms, pr=unique(prob))
    return(ATES)
  }
  #then apply to all the vars
  ans <- sapply(df[c(vars)], Ates)
  return(ans)
}

```

### 3-4

```{r results='asis'}

PvalueTable <- function(df, perm, probs, means_table, vars) {
  

  #the estimates matrix (we want the absulute values)
  estimate <- abs(EstFunc(df,perm,probs,vars))
  
  #the actual means diffrence between the treat and control
  actual_diff <- abs(t(means_table["effect"]))
  
  #now we want to check how many values are higher (because its absulute we dont     care about the lower)
  raw_data <- c()
  for (col in colnames(actual_diff)) {
    counter <- sum(estimate[,c(col)] >= actual_diff[,c(col)])/10000
    raw_data <- c(raw_data, counter)
  }
  p_value_data <- data.frame(parameter = colnames(actual_diff), p_val =raw_data)
  #order the p_values
  p_value_data <- p_value_data[order(p_value_data$p_val),]
  #the total p_value
  p_value_data <- rbind(p_value_data, c("Total", round(mean(p_value_data$p_val), 4)))
  #making the numbers precentages
  p_value_data$p_val <- percent(as.numeric(p_value_data$p_val))
  return(p_value_data)
}

P_val_Total <- PvalueTable(df, permutations, probs, means_table, vars)
stargazer(t(P_val_Total),type="html",flip=T,title="P-Values for all 14 variables")
```

### 5

We can see that in total 37% of the treatment effects in the distribution that we created were at least as extreme (either as vigorous or negative).

It means that in total we cannot reject the null hypothesis with good level of confidence (5% or 10%).

But if we will look at the parameters separately, we can see that IQ and college parameters are actually less than 10-5% so we can inference that the treatment actually do make this parameters better - children will go more to school and have a better IQ as we will go down the table below, the P-value is getting higher and therefor a low significant to reject the null hypothesis (like the employed, parent, iep12, hsgrad and jailed parameter).

```{r, echo=FALSE}
stargazer(means_table,type="text",title="Estimated average treatment effects", digits=2,summary = FALSE, covariate.labels = c("Var","Mean treated", "Mean not treated", "Avrage treatment effect"), out.header=TRUE)
```

As for the parameters that got 100%, lets remember that in our table with the difference in means in section 2, we saw that this parameters(convicted, felon, jailed, marijuana), have a minimal difference between the treated and not treated.

So we can say that the treatment is effective but not in all the parameters.

### 6

```{r results='asis'}
#Ive just took the process above and automate it with functions
PermProbs <- function(table) {
  permutations <- genperms(table$treat, blockvar=NULL, clustvar=NULL)
  probs <- genprobexact(table$treat, clustvar = table$SUBJECT)
  return(list(permutations, probs))
}

dfMale <- subset(df, df$fem==0)
dfFemale <- subset(df, df$fem==1)

M_perms_probs <- PermProbs(dfMale)
F_perms_probs <- PermProbs(dfFemale)

P_val_Males <- PvalueTable(dfMale, M_perms_probs[[1]], M_perms_probs[[2]], means_table_M, vars)
P_val_Females <- PvalueTable(dfFemale, F_perms_probs[[1]], F_perms_probs[[2]], means_table_F, vars)

stargazer(t(P_val_Males),type="html",flip=T,title="P-Values for all 14 variables-Only Males")

stargazer(t(P_val_Females),type="html",flip=T,title="P-Values for all 14 variables-Only Females")
```

Lets try to see what are the differences with boys and girls:

It seems like the IQ at younger ages (5, 6) is improved better at boys then girls, but the IQ of girls at older age (15) improved more then boys.

We can see that the employment is impacted more at the boys group then the girls (19.8%\<36.28%).

it looks like the males are more effected by the "crime" parameters than girls (probably because girls from the first place are less involved in crime).

In conclusion there is a slight difference between boys and girls in some variables.
