---
title: "52414 - lab 1"
author: "Polke Matan and Lourie Yonatan"
date: "23/5/2021"
output:
    rmarkdown::github_document:
    theme: journal
    toc: true
    toc_depth: 2
    df_print: paged
---
```{r, include=FALSE}
library(tidyverse) # This includes dplyr, stringr, ggplot2, .. 
library(data.table)
```
### 1.
Read the data, make the date column as datetype, make an ID column.

```{r}
df <- read.csv("owid-covid-data.csv")
df$date <- as.Date(df$date)
df$ID <- seq.int(nrow(df))
class(df$date)
```

### 2.

First of all, ive created a function that will omit NA data only from the desired variables. Then, i made a function that will: run the aggregate function for every country to find the maximum total cases per million, and sorted it by the total cases value. Ive extracted the top 5 countries. Then i did the same procedure to find the minimum date of each one of the countries. At the end, ive joined both of the dataframes, and filtered only the top 5 countries that i found. at the end i will loop over all the desired vars and deploy the function for each one of them.


```{r}
OmitCertainCols <- function(data, desiredCols) {
  completeVec <- complete.cases(data[, desiredCols])
  return(data[completeVec, ])
}


  ex2 <- function(var) {
    df <- OmitCertainCols(df,c("location", "date", var))
    top_counry_df <- aggregate(df[var], by=list(df$location), max)
    top_counry_df <- na.omit(top_counry_df)
  top_counry_df <- top_counry_df[order(-top_counry_df[, var]),]
  colnames(top_counry_df) <- c("location", var)
  
  top_countries <- top_counry_df[order(-top_counry_df[, var]),]$location[1:5]
  last_date <- aggregate(df$date, by=list(df$location), max)
  colnames(last_date) <- c("location", "last_date")
  
  total_cases_ans <- subset(left_join(top_counry_df, last_date, by="location"), location %in% top_countries)
  
  return(total_cases_ans)
    
}
lst <- c("total_cases_per_million", "total_deaths_per_million", "total_vaccinations_per_hundred" )
for (par in lst) {
  print(ex2(par))
}
```

We can see the three tables with the desired values.


### 3. 
#### a.
The function arguments are dataframe and string(name of a column in the dataframe).
In the first few rows, the function is cleaning missing values, filtering values that are less from zero.
The if and else statement are just to make the function more flexible.
Ive figure out from the data that for every continent the ISO_code is starting with OWID, so i filtered by that.
Then its just a simple ggplot function.
*I added a function that calculate the difference between min and max date in months.

```{r}
months_diff <- function(end_date, start_date) {
    ed <- as.POSIXlt(end_date)
    sd <- as.POSIXlt(start_date)
    12 * (ed$year - sd$year) + (ed$mon - sd$mon)
}


ex3a <-  function(df,col){
  df1 <- filter(df, df[col]>0)
  if (any(names(df1) == "continent")) {
    df1 <- OmitCertainCols(df1,c("date", col, "continent"))

    
  }
  else {
    df1 <- OmitCertainCols(df1,c("date", col, "location"))
  }
  
  
  if (any(names(df1) == "iso_code")) {
    df1 <- df1[grepl("^OWID", df1$iso_code) & df1$location %in% c("Africa", "Asia","Europe","North America","South America", "Oceania"),]  
 
  }
  
  
months <- round(months_diff(max(df1$date),min(df1$date))/10)+1


ggplot(df1,aes_string(y=col,col="location"))+ geom_line(aes(x=as.Date(date)), size=0.8,alpha=0.99)+ylab(gsub("_"," ",col))+xlab("date")+ scale_x_date(date_labels = "%m-%Y", date_breaks = paste0(months, " month")) +ggtitle(paste0(col, " per continent")) +scale_color_brewer(palette ="Dark2")
}

```




#### b.

```{r}
ex3a(df, "new_cases")
```
From the graph above, we can see the first peak in Asia at March 2020, then a peak in Europe.
We can also see clearly the dramatic rise in Asia which probably refer to India in the last month.
because the graph is not in logarithmic scale, the newest cases looks much higher than what happened year ago and its really hard to see the real pattern.


In the column new_cases_smoothed we have negative values that will be NA after the log transformation, so I added a constant to the whole dataset.
There is alot of way to deal with negative data in a log transformation, but i find this way most straightforward and clean.

```{r}
log_transofrmer <- function(df, col, new_col) {
  df <- subset(df, df[col]>0)
  min_val <- min(na.omit(df[col]))
  df[col] <- df[col] + abs(min_val)
  df[new_col] <- log(df[col])
  return(df)
}

dfex3a <- df
dfex3a <- log_transofrmer(df, "new_cases_smoothed", "new_cases_smoothed_log")
ex3a(dfex3a, "new_cases_smoothed_log")


```

Its easy to see that is much more easier to interpret the smooth log plot of new cases. 
The data is smooth by 7 days - which means that we will see less "steps" in the data.
When we care about relative change - is better to use the logarithmic scale, and when we care about **absolute** change we will use the original linear data.
In our case we want to see the patrtren of the new cases so its smarter to use the logarithmic scale.


```{r}
dfex3b <- df
dfex3b <- log_transofrmer(df, "new_deaths_smoothed", "new_deaths_smoothed_log")

ex3a(dfex3b, "new_deaths_smoothed_log")


dfex3b <- df
dfex3b <- log_transofrmer(df, "new_vaccinations_smoothed", "new_vaccinations_smoothed_log")

ex3a(dfex3b, "new_vaccinations_smoothed_log")




```
The pattern of new deaths looks pretty correlate with Eurpoe and North America. We can see clearly the "Waves" at each continent. and we can also see how that in all continent (Except from Asia), the numbers are going down.

In the new vaccination graph we can see the same pattern - sharp rise when in the begining, and then convergence to a more moderate line.

### 4

The function is subsetting a  certain continent data, and then applying a sum function by date for every date.
The output is a dataframe with columns: date, InputColumn, continent.
#### a.

```{r}

ex4a  <-  function(df,col){
  df <- OmitCertainCols(df,c("location"))
  # df <- subset(df, continent != "")
  continents=c("Africa", "Asia","Europe","North America","South America", "Oceania")
  ContinentData=data.frame()
  tmp.data=data.frame()
  
  for(c in c(continents)){
    ConDate <- df %>% filter(continent == c |location==c)
    ConDate <- ConDate[c("date", col)]
    ConDate[is.na(ConDate)] <-  0
    
    colnames(ConDate) <- c("date", "x")
    agg1 <- aggregate(ConDate$x, by=list(ConDate$date), sum)
    
    agg1$continent=c
    ContinentData=rbind(ContinentData,agg1)
  }
  colnames(ContinentData)=c("date", col,"continent")
  return(ContinentData)
}

```


#### b. 

```{r}
ex4b_df <- ex4a(df, "new_tests_smoothed")
ex4b_df$location <- ex4b_df$continent  


dfex4b <- log_transofrmer(ex4b_df,"new_tests_smoothed", "new_tests_smoothed_log")

ex3a(dfex4b, "new_tests_smoothed_log")
```

### 5

I made tow tables for each one of the variables, then joined them together and ploted the scatterplot + the abline of the regression.
#### a.

```{r}
df_ <- OmitCertainCols(df, c("total_cases_per_million", "total_deaths_per_million"))
ex5Model <- lm(total_deaths_per_million ~total_cases_per_million, data=df)
MaxCasesPerMillion <- aggregate(total_cases_per_million~location , df, FUN = max)
MaxDeathsPerMillion <- aggregate(total_deaths_per_million~location , df, FUN = max)
ex5_df <- full_join(MaxCasesPerMillion, MaxDeathsPerMillion, by="location")
ggplot(ex5_df, aes(x=total_cases_per_million, y=total_deaths_per_million)) + geom_point() +  stat_smooth(method = "lm", col = "red")


```

The slope is `r ex5Model$coefficients[2]` which mean that for every case only a fraction of `r ex5Model$coefficients[2]` will be dead. For example, for every 10,000 people who got corona, only `r ex5Model$coefficients[2]*10000` will die.

#### b.

```{r}
df_ex5 <- OmitCertainCols(df, c("new_cases","new_deaths", "date", "location" ))
ex5b_df_case <- df_ex5 %>%
  group_by(location) %>%
  top_n(n=1,wt= new_cases)


ex5b_df_case <- ex5b_df_case[!duplicated(ex5b_df_case[ , c("location","new_cases")]),]
date_cases <- ex5b_df_case[c("location", "date")]

ex5b_df_death <- df_ex5 %>%
  group_by(location) %>%
  top_n(n=1, wt=new_deaths)

ex5b_df_death <- ex5b_df_death[!duplicated(ex5b_df_death[ , c("location","new_deaths")]),]
date_deaths <- ex5b_df_death[c("location", "date")]

ex5b_df <- full_join(date_cases, date_deaths,by="location")
names(ex5b_df) <- c("location", "date_cases", "date_deaths")



ggplot(ex5b_df, aes(x=date_cases, y=date_deaths)) + geom_point() +  stat_smooth(method = "lm", col = "red")



ex5b_df$date_cases <- as.numeric(ex5b_df$date_cases)
ex5b_df$date_deaths <- as.numeric(ex5b_df$date_deaths)
ex5bModel <- lm(date_cases~date_deaths, data=ex5b_df)
summary(ex5bModel)

```



The slope is `r ex5bModel$coefficients[2]`. is not that close to one because probably there is not that high correlation between the tow variables. BUT, its really make sense that after a few weeks from the date with maximum new cases, it will be the date with the maximum dates.
I think that is the reason that we dont have better correlation. The intercept is not that informative here.


### 6
In this question I filterd the relvenat columns to new df for each column
("new_cases",'new_deaths','new_vaccinations'). Then I summed each relevant 
column, by month, and combined to a df called "monthly"

```{r}
df6 <- OmitCertainCols(df,c("continent"))
q6 <-df6[c("date","new_cases",'new_deaths','new_vaccinations')]
q6[is.na(q6)]<-0
q6$monyear <- strftime(q6$date, "%Y-%m") 
q6a <- aggregate(new_cases ~ monyear, q6, FUN = sum)
q6b <- aggregate(new_deaths ~ monyear, q6, FUN = sum)
q6c <- aggregate(new_vaccinations ~ monyear, q6, FUN = sum)
monthly <- cbind(q6a,q6b[2],q6c[2])
monthly

ggplot(monthly,aes(x=monyear,y=new_cases))+geom_bar(stat = "identity") + ggtitle("Global new cases per month") +
scale_y_continuous(labels = scales::unit_format(unit = "M", scale = 1e-6)) +
  theme(axis.text.x= element_text(angle = 90, vjust = 0.5, hjust=1))
ggplot(monthly,aes(x=monyear,y=new_deaths))+geom_bar(stat = "identity") + ggtitle("Global new deaths per month") +
scale_y_continuous(labels = scales::unit_format(unit = "M", scale = 1e-6)) +
  theme(axis.text.x= element_text(angle = 90, vjust = 0.5, hjust=1))
ggplot(monthly,aes(x=monyear,y=new_vaccinations))+geom_bar(stat = "identity") + ggtitle("Global new vaccinations per month") +
scale_y_continuous(labels = scales:: unit_format(unit = "M", scale = 1e-6)) +
  theme(axis.text.x= element_text(angle = 90, vjust = 0.5, hjust=1))


```


we can see the barplots showing us by months the info ("new_cases",'new_deaths','new_vaccinations') in the df monthly, in millions.



### 7:
I add to the data frame the column deathrate, which is the  number created form the number of deaths divided divided by the number of cases the country had so far.
then I made a histgram shows the up to date death rate, and listed the 3 countries with the highest death rate.

```{r}

df <- OmitCertainCols(df,c("total_cases","date","location","total_deaths"))
df['death_rate'] <- df["total_deaths"]/df["total_cases"]
q7 <- df %>% filter(date == "2021-05-04")
qplot(q7$death_rate,geom = "histogram",bins=50, main = "current global death rate by country",xlab = "Death Rate",ylab = "Number of countries")
q7 <- q7[,c("location","date","death_rate")]
q7 %>% top_n(3, death_rate)
```
we can see that almost all of the death rates are under 5%.
we can see a table of the 3 countries with the highest death rate.

### 8:
I've added to df a new column thats shows the percent of fully vaccinated people out of all vaccinated people. Then, I filtered the result of the two dose fraction along time of USA,UK and Israel.

```{r}
df['two_dose_fraction'] <- df["people_fully_vaccinated"]/df["people_vaccinated"]
q8 <-df[c("date","location","two_dose_fraction")]
q8 <- q8 %>% filter(location == "Israel"|location == "United Kingdom"|location == "United States" )
q8 <- q8 %>% na.omit()
ggplot(q8,aes_string(y='two_dose_fraction', col="location"))+ ggtitle("Two dose vaccination % by country and date") + geom_line(aes(x=as.Date(date))) + xlim(as.Date("2020-11-01"), as.Date("2021-05-04"))
```

we can see that Israel and USA have a similar stratagey,just Israel began first.we can see the strategy is to fully vaccine each person which is vaccined, because the line is going up.
The UK line is going down from mid January, which shows us that there are taking a big gap bewtween the two vaccines for every person.

### 9
#### a.
In this function I will create a vector length of 121.from -60 to 60. each number is represnting the days gap between two columns we receive. we will run over all the days inside our range of dates the are the gap of dates. crate two vectors and check the correlation between them.

```{r}
ex9a <- function(df,loc,col1,col2){
  vector_ans <- c()
  q9 <- subset(df,location == loc)
  q9 <- q9[,c(all_of(col1),all_of(col2),"date", "location")]
  start_date <- min(q9$date)
  fin_date <- max(q9$date)
  for (i in seq(60,0,-1)){
    dxt <-  seq(start_date+i , fin_date,by="days")
    dyt <-  seq(start_date , fin_date-i,by="days")
    vecx <- q9 %>% filter(date %in% dxt) %>% select(all_of(col1))
    vecy <- q9 %>% filter(date %in% dyt) %>% select(all_of(col2))
    vector_ans <- c(vector_ans,cor(vecx,vecy,use="complete.obs"))
    }
  for (i in c(1:60)){
    dxt <-  seq(start_date , fin_date-i,by="days")
    dyt <-  seq(start_date+i , fin_date,by="days")
    vecx <- q9 %>% filter(date %in% dxt) %>% select(all_of(col1))
    vecy <- q9 %>% filter(date %in% dyt) %>% select(all_of(col2))
    vector_ans <- c(vector_ans,cor(vecx,vecy,use="complete.obs"))
  }

  return(vector_ans)
}
```

#### b.
use function from 9a at 9b for Canada, new cases and new deaths

```{r}
Canada_cor <- ex9a(df,"Canada","new_cases","new_deaths")
Days_gap <- seq(-60,60,1)
data_9 <- data.frame(cbind(Days_gap,Canada_cor))
ggplot(data_9,aes(x=Days_gap,y=Canada_cor)) + geom_point()+ ggtitle("Candas cor between new deaths and cases") 
```
we can see on the plot that the highest correlation between new cases and death is with +15 days gap. the distribution is close to normal with a left tail.

### 10
Ive gather the data separately and joined it all by location (put a note that there is alot of nulls with the vaccinations per hundred, i assumed that those countries have vaccinated yet).
Then i plotted the result with ggplot and made israel an UK in red.

```{r}
dfex10 <- OmitCertainCols(df, c("date", "new_cases_smoothed"))
dfex10 <- subset(dfex10, continent!="")
current_newCases <- subset(dfex10, date=="2021-04-23")[,c("location", "new_cases_smoothed", "population")]
maximal_newCases <- aggregate(new_cases_smoothed~location, dfex10, FUN=max)
total_Vacc <- subset(dfex10, date=="2021-04-01")[,c("location", "total_vaccinations_per_hundred", "population")]



ratioMaker <- full_join(current_newCases, maximal_newCases, by="location")

ratio <- ratioMaker$new_cases_smoothed.x/ratioMaker$new_cases_smoothed.y
ratioMaker$ratio <- ratio


results_table <- full_join(ratioMaker[,c("location", "ratio")],total_Vacc, by="location" )
results_table[,c("ratio")] <-  log(results_table[,c("ratio")])

ggplot(data=results_table, aes(x=total_vaccinations_per_hundred, y=ratio, label=location)) + geom_point()+ geom_point(data=results_table[results_table$location %in% c("Israel","United Kingdom"),],color="red") +geom_text(aes(label=ifelse(location %in% c("Israel","United Kingdom"),as.character(location),'')),hjust=0.4,vjust=-1)+ ggtitle("Vaccination effect on new cases") 


```



We can see that IL and UK did a lot of vaccination and the ratio of $\frac{Current(New\_cases)}{Max(new\_cases)}$ is pretty low. which means that the vaccinations have a good impact on the ratio of new cases. 
If we will look at the countries with the same number of vaccinations it seems like there is worst ratio of new cases.
I plotted the data again but now with the size of the population:

```{r}
lab_counties <- c("Israel","United Kingdom")
biggest <- top_n(results_table, 3, wt=population)$location
mostVacc <- top_n(results_table, 3, wt=total_vaccinations_per_hundred)$location
GoodRatio <- top_n(na.omit(results_table), 5, wt=-ratio)$location


ggplot(data=results_table, aes(x=total_vaccinations_per_hundred, y=ratio, label=location,size=population)) + geom_point()+


geom_point(data=results_table[results_table$location %in% biggest,],color="blue") +geom_text(aes(label=ifelse(location %in% biggest,as.character(location),'')),hjust=0.4,vjust=-1, size=4)+ 
  
geom_point(data=results_table[results_table$location %in% mostVacc,],color="green") +geom_text(aes(label=ifelse(location %in% mostVacc,as.character(location),'')),hjust=0.4,vjust=-1, size=4)+ 
  
geom_point(data=results_table[results_table$location %in% GoodRatio,],color="purple") +geom_text(aes(label=ifelse(location %in% GoodRatio,as.character(location),'')),hjust=0.4,vjust=-1, size=4)+ 
  
geom_point(data=results_table[results_table$location %in% lab_counties,],color="red") +geom_text(aes(label=ifelse(location %in% lab_counties,as.character(location),'')),hjust=0.4,vjust=-1, size=4)+ 
 guides(color = guide_legend(override.aes = list(linetype = c(1, 0) ) ) )+
theme_bw() +theme(legend.position="none")+

  ggtitle("Vaccination effect on new cases") 

```



Blue - biggest countries, Purple - best ratio, Green - Most vaccinated.
We can see the great difference in the raio between China and India (which have almost the same size, same vaccination).
I think that the problem with this comparison is that we need also take in consideration the velocity of the vaccination (in Israel the vaccination operation ended in a ~month).

